env_and_copies_stats

### 2023-03-20 code/analysis_code/stats/uni_variate.qmd
stats

```{r}
master<- 
  dust %>% full_join(data) %>%
  filter(hr_cst %in% "01") #While this is technically not for hour 1, this gets ride of all duplicates for the sake of analysis.

master<- master %>%
  select(copies_mL, t7sum, site, date) 
```

@@

# Multivariate Models

[This code is still in progress. For now, please ignore:]{.ul}

#### Make New Dataset

```{r}
master2<- dust0 %>% full_join(data) %>%
  filter(hr_cst %in% "01") %>%
  select(site, sal, temp, amm, nn,orthop, copies_mL, t7sum) %>%
  na.omit()
```

#### Site-specific Data sets

```{r}
bo_a<- master2 %>%
  filter(site %in% "Blind Oso") %>%
  select(!site)

c2_a<- master2 %>%
  filter(site %in% "Canals")%>%
  select(!site)

rd_a<- master2 %>%
  filter(site %in% "Gulf")%>%
  select(!site)
```

## BO: Using all Variables vs. Growth

```{r}
#Create Recipe for Growth and all other parameters
growth_recipe_bo<- recipe(copies_mL ~ ., data = bo_a)

#Set up linear model
lm_mod_all<- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")

#Workflow that adds recipe to model
Growth_wflow<- 
  workflow() %>%
  add_model(lm_mod_all) %>%
  add_recipe(growth_recipe_bo)

#Use workflow to fit model to  data set
growth_fit_bo<- Growth_wflow %>%
  fit(data = bo_a)

#Pull model fit using parsnip()
growth_fit_bo %>%
  extract_fit_parsnip() %>%
  tidy()
```

Plot

```{r}
tidy(growth_fit_bo) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```
### Use model to test data

```{r}
aug_test_bo_a <- augment(growth_fit_bo, bo_a)
```

```{r}
rmse <- aug_test_bo_a %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_bo_a %>% rsq(truth = copies_mL, .pred)
bo_a_metrics<- full_join(rmse, rsq)
```

```{r}
bo_a_mod<- lm(copies_mL ~ ., data = bo_a)
AIC(bo_a_mod)
```

```{r}
res_bo_a<- resid(bo_a_mod)
plot(fitted(bo_a_mod), res_bo_a)
abline(0,0)
```
## C2: Using all Variables vs. Growth

```{r}
#Create Recipe for Growth and all other parameters
growth_recipe_c2<- recipe(copies_mL ~ ., data = c2_a)

#Set up linear model
lm_mod_all<- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")

#Workflow that adds recipe to model
Growth_wflow<- 
  workflow() %>%
  add_model(lm_mod_all) %>%
  add_recipe(growth_recipe_c2)

#Use workflow to fit model to  data set
growth_fit_c2<- Growth_wflow %>%
  fit(data = c2_a)

Plot

```{r}
tidy(growth_fit_c2) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```
### Use model to test data

```{r}
aug_test_c2_a <- augment(growth_fit_c2, c2_a)
```

```{r}
rmse <- aug_test_c2_a %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_c2_a %>% rsq(truth = copies_mL, .pred)
c2_a_metrics<- full_join(rmse, rsq)
```

```{r}
c2_a_mod<- lm(copies_mL ~ ., data = c2_a)
AIC(c2_a_mod)
```

```{r}
res_c2_a<- resid(c2_a_mod)
plot(fitted(c2_a_mod), res_c2_a)
abline(0,0)
```
## RD: Using all Variables vs. Growth

```{r}
#Create Recipe for Growth and all other parameters
growth_recipe_rd<- recipe(copies_mL ~ ., data = rd_a)

#Set up linear model
lm_mod_all<- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")

#Workflow that adds recipe to model
Growth_wflow<- 
  workflow() %>%
  add_model(lm_mod_all) %>%
  add_recipe(growth_recipe_rd)

#Use workflow to fit model to  data set
growth_fit_rd<- Growth_wflow %>%
  fit(data = rd_a)

Plot

```{r}
tidy(growth_fit_rd) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))
```
### Use model to test data

```{r}
aug_test_rd_a <- augment(growth_fit_rd, rd_a)
```

```{r}
rmse <- aug_test_rd_a %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_rd_a %>% rsq(truth = copies_mL, .pred)
rd_a_metrics<- full_join(rmse, rsq)
```

```{r}
rd_a_mod<- lm(copies_mL ~ ., data = rd_a)
AIC(rd_a_mod)
```

```{r}
res_rd_a<- resid(rd_a_mod)
plot(fitted(rd_a_mod), res_rd_a)
abline(0,0)
```

>>>>

```{r}
master0<- 
  dust %>% full_join(data) %>%
  filter(hr_cst %in% "01") #While this is technically not for hour 1, this gets ride of all duplicates for the sake of analysis.

master<- master0 %>%
  select(copies_mL, t7sum, site, date) 
```

@@

# TEMPERATURE

### Blind Oso

```{}
```
